---
subtitle: A quantitative appraisal of CMR publications
description: This document reports on a systematic search which explores the landscape of cardiac magnetic resonance (CMR)-related publications in the last years (2017-2024).
format:
  dashboard: default
execute:
  echo: false
  output: true
  error: false
  warning: false
  freeze: false
width: 100%
---
```{r fetch-data}
source("scripts/data-fetch.R")
source("scripts/authors-fetch.R")
```

# Journals
- A total of `r nrow(journals_card)` journals in the *Cardiology and Cardiovascular Medicine* category, and `r nrow(journals_rad)` journals in the *Radiology, Nuclear Medicine and Imaging* category were identified as the top 10% journals in their respective category (n = `r nrow(journals_all)` total journals).
  - of these, `r nrow(journals_all_CMR)` journals had articles related to CMR.

```{r view-journals}
library(DT)
datatable(journals_all_CMR[,])
```

# Papers
- Between 2017 and 2024, a total of `r results$Articles` CMR-related papers were published. Of these, `r nrow(papers_cmr)` (`r round(nrow(papers_cmr) / papers_n * 100, digits = 1)`%) were published in top 10% journals by a total of `r length(first_authors_cmr_unique)` unique first authors and `r length(last_authors_cmr_unique)` unique last authors.

```{r}
# get insights about these data:
S <- summary(object = results, k = 10, pause = FALSE)
#plot(x = results, pause = T) # not working
```

```{r}
threeFieldsPlot(papers_)
# fetch journals with abbreviations
```

## Donut about document types
```{r donut}
library(echarts4r)
library(stringr)
df <- results$Documents |> as.data.frame()

# Modify the levels of Var1 by searching for substrings
levels(df$Var1) <- sapply(levels(df$Var1), function(x) {
  case_when(
    x == "REVIEW                               " ~ "Review",
    str_detect(x, "TRIAL") ~ "Clinical trial",
    str_detect(x, "MULTICENTER") ~ "Multicenter study",
    str_detect(x, "META-ANALYSIS") ~ "Meta-analysis",
    str_detect(x, "SYSTEMATIC") ~ "Systematic review",
    str_detect(x, "STUDY") ~ "Clinical study",
    str_detect(x, "ABSTRACT") ~ "Abstract",
    str_detect(x, "JOURNAL ARTICLE") ~ "Journal article (not specified)",
    str_detect(x, "LETTER|REPORT|EDITORIAL|CONSENSUS|NEWS") ~ "Other",
    TRUE ~ x  # Keep the level unchanged if it doesn't match any condition
  )
})

# Convert back to a factor to ensure it's still a factor
df$Var1 <- factor(df$Var1)

# Drop any unused levels to remove redundancies
df$Var1 <- droplevels(df$Var1)

df %>%
  group_by(Var1) %>%
  summarize(Freq = sum(Freq)) %>%
  ungroup() |> 
  e_charts(Var1) |> 
  e_pie(Freq, radius = c("50%", "70%")) |> 
  e_title("Donut chart")

```

```{r wordcloud}
terms <- attr(results$ID, "dimnames")[[1]]
freqs <- as.numeric(results$ID)

df <- data.frame(
  term = terms,
  frequency = freqs
)

df |> 
  e_color_range(frequency, color) |> 
  e_charts() |> 
  e_cloud(term, frequency, color, shape = "circle", sizeRange = c(10, 150)) 
```

# Authors

```{r view-papers}
last_authors_cmr <- readxl::read_xlsx("data/table-last-authors.xlsx")
datatable(last_authors_cmr)
```

## Last authors by affiliation

```{r authors-affil}
last_author_cmr_location <- read_xlsx("data/table-last-authors-location.xlsx")
```

## Last authors by specialty
```{r}
last_authors_cmr <- last_authors_cmr |> 
  mutate(primary_specialty_assigned = case_when(
    primary_specialty_assigned == "Non-MD scientist" |
    primary_specialty_assigned == "NA" ~ "Non-MD or unassigned",
    primary_specialty_assigned == "Radiology"  ~ "Radiology", 
    primary_specialty_assigned == "Cardiology"  ~ "Cardiology"
  ))

library(ggplot2)
ggplot(last_authors_cmr, aes(x=as.factor(primary_specialty_assigned))) +
  geom_bar(color="black", fill=rgb(0.1,0.4,0.5,0.7) )+ylab("Count")+xlab("Assigned specialty")

cards <- sum(last_authors_cmr$primary_specialty_assigned=="Cardiology", na.rm = T)
rads <- sum(last_authors_cmr$primary_specialty_assigned=="Radiology", na.rm = T)
nonmd <- sum(last_authors_cmr$primary_specialty_assigned=="Non-MD scientist", na.rm = T)
others <- sum(last_authors_cmr$primary_specialty_assigned=="Unassigned", na.rm = T)
```

- a total of `r cards` authors specializing in Cardiology and `r rads` authors specializing in Radiology were identified worldwide.
- Specialty was not assigned to `r others` due to paucity of data.

## Author map

```{r author-map}
source("R/map-authors.R")
p
```
