---
title: CMR publications 2019 to 2024
subtitle: A quantitative appraisal
description: This document reports on a systematic search conducted on 5th August 2024 which explored the landscape of cardiac magnetic resonance (CMR)-related publications in the last 5 years (2019-2024).
format: 
  dashboard:
    page-layout: full
    toc: true
    toc-location: left
execute:
  echo: false
  output: true
  error: false
  warning: false
  freeze: false
width: 100%
---
```{r fetch-data}
source("scripts/data-fetch.R")
source("scripts/authors-fetch.R")
```

# Methods
- Systematic search of all CMR-related studies indexed on [PubMed](https://pubmed.ncbi.nlm.nih.gov) as of 8th August 2024
- Journal search restricted to top 10% journals in cardiology and radiology on the [Scopus database](https://www.scopus.com/)
- Author search restricted to first and last authors with at least 2 CMR-related publications.

# Journals
- A total of `r nrow(journals_rad)` journals in the *Cardiology and Cardiovascular Medicine* category, and `r nrow(journals_rad)` journals in the *Radiology, Nuclear Medicine and Imaging* category were identified. 
- `r nrow(journals_all_CMR)` journals had articles related to CMR.

```{r view-journals}
library(DT)
datatable(journals_all_CMR[,])
```

# Papers
- Between 2019 and 2024, a total of `r results$Articles` CMR-related papers were published. Of these, `r nrow(papers_cmr)` (`r round(nrow(papers_cmr) / papers_n * 100, digits = 1)`%) were published in top 10% journals by a total of `r length(first_authors_cmr_unique)` unique first authors and `r length(last_authors_cmr_unique)` unique last authors.

# Authors
```{r view-papers}
datatable(as.data.frame(table(prolific_cmr_authors)))
```
