---
title: CMR publications 2019 to 2024
subtitle: A quantitative appraisal
description: This document reports on a systematic search conducted on 5th August 2024 which explored the landscape of cardiac magnetic resonance (CMR)-related publications in the last 5 years (2019-2024).
format: 
  dashboard:
    page-layout: full
    toc: true
    toc-location: left
execute:
  echo: false
  output: true
  error: false
  warning: false
  freeze: false
width: 100%
---
```{r fetch-data}
source("scripts/data-fetch.R")
source("scripts/authors-fetch.R")
```

# Journals
- Journal search on Scopus was restricted to the top 10% journals in cardiology and radiology on the [Scopus database](https://www.scopus.com/)
- A total of `r nrow(journals_card)` journals in the *Cardiology and Cardiovascular Medicine* category, and `r nrow(journals_rad)` journals in the *Radiology, Nuclear Medicine and Imaging* category were identified as the top 10% journals in their respective category (n = `r nrow(journals_all)` total journals).
  - of these, `r nrow(journals_all_CMR)` journals had articles related to CMR.

```{r view-journals}
library(DT)
datatable(journals_all_CMR[,])
```

# Papers
- A systematic search was conducted for all CMR-related studies indexed on [PubMed](https://pubmed.ncbi.nlm.nih.gov) as of `r Sys.Date()` with a date of publication between 2017 to 2024.
- Between 2019 and 2024, a total of `r results$Articles` CMR-related papers were published. Of these, `r nrow(papers_cmr)` (`r round(nrow(papers_cmr) / papers_n * 100, digits = 1)`%) were published in top 10% journals by a total of `r length(first_authors_cmr_unique)` unique first authors and `r length(last_authors_cmr_unique)` unique last authors.

# Authors
- Author search on Scopus was limited to first and last authors with > 1 CMR-related publications.

```{r view-papers}
datatable(as.data.frame(table(prolific_cmr_authors)))
```

# Authors by affiliation

# Authors by specialty
- Specialty was inferred through combination of automated and manual searches based on Google search results.
- Cardiology as the main specialty was inferred if the author's CV or relevant online statements (e.g. LinkedIn) referred to a clinical fellowship or professorship in cardiology; if any statements were retrieved that the author is an expert in clinical electrophysiology, interventional cardiology, and/or heart failure; if the author's ResearchGate profile listed clinical cardiology among the author's interests.
- Radiology as the main specialty was inferred if the author's CV or relevant online statements (e.g. LinkedIn) referred to a fellowship or professorship in radiology; if the author was affiliated to a department of radiology and published on imaging subjects different than cardiovascular imaging; if the author's ResearchGate profile listed radiology as the author's interest.


